Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-19 WSSSPE3/report/wg_appendix_publishing_SW.tex
Reformatted group members to itemized list to ensure they appear in the right place.
Former-commit-id: e4584de998d67127bdd327661163fca316f83c01
adding POC request to appendices
Former-commit-id: 42aa40a42eb82bf40df6e482de5fb48dc9085b8d
Added myself as POC

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   Steven R. Brandt & Louisiana State University
\\ Daniel Gunter    & LBNL
\\ Yuhan Ding       & Illinois Institute of Technology
\\ Neil Chue Hong   & Software Sustainability Institute
\end{longtable}
}

>>>>

Steven R. Brandt\footnote{email: \href{mailto:sbrandt@cct.lsu.edu}{sbrandt@cct.lsu.edu}} will serve as the point of contact for this working group.

\subsection{Group Members}

\begin{itemize}
\item Steven R. Brandt -- Louisiana State University
\item Daniel Gunter -- LBNL
\item Yuhan Ding -- Illinois Institute of Technology
\item Neil Chue Hong -- Software Sustainability Institute
\end{itemize}
